\documentclass[11pt]{scrartcl}
\usepackage[sexy]{evan}
\usepackage{answers}

\begin{document}
\title{Nepal TST 2025 Solutions}
\author{Prakrit Gajurel}
\date{28 June 2026}
\maketitle

\section{Day 1 Problems}

\begin{problem}
    Consider a triangle $\triangle ABC$ and some point $X$ on $BC$. The perpendicular from
    $X$ to $AB$ intersects the circumcircle of $\triangle AXC$ at $P$ and the perpendicular
    from $X$ to $AC$ intersects the circumcircle of $\triangle AXB$ at $Q$. Show that the
    line $PQ$ does not depend on the choice of $X$.
\end{problem}

\begin{proof}
    
\end{proof}

\begin{problem}
    Find all integers $n$ such that if
    \[
    1 = d_1 < d_2 < \cdots < d_{k-1} < d_k = n
    \]
    are the divisors of $n$, then the sequence
    \[
    d_2 - d_1,\, d_3 - d_2,\, \ldots,\, d_k - d_{k-1}
    \]
    forms a permutation of an arithmetic progression.
\end{problem}

\begin{proof}
    
\end{proof}

\begin{problem}
    Find all functions $f : \mathbb{R}^+ \rightarrow \mathbb{R}^+$ such that
    \[f(f(x)) + xf(xy) = x + f(y)\]
    for all positive real numbers $x$ and $y$.
\end{problem}

\begin{proof}
    
\end{proof}

\newpage

\section{Day 2 Problems}

\begin{problem}
    Let the sequence $\{a_n\}_{n \geq 1}$ be defined by
    \[
    a_1 = 1, \quad a_{n+1} = a_n + \frac{1}{\sqrt[2024]{a_n}} \quad \text{for } n \geq 1, \, n \in \mathbb{N}
    \]
    Prove that
    \[
    a_n^{2025} >n^{2024}
    \]
    for all positive integers $n \geq 2$.
\end{problem}

\begin{proof}
    
\end{proof}

\begin{problem}
    Kritesh manages traffic on a $45 \times 45$ grid consisting of 2025 unit squares. Within each unit square is a car, facing either up, down,
    left, or right. If the square in front of a car in the direction it is facing is empty, it can choose to move forward. Each car wishes to exit
    the $45 \times 45$ grid.

    Kritesh realizes that it may not always be possible for all the cars to leave the grid. Therefore, before the process begins, he will 
    remove $k$ cars from the $45 \times 45$ grid in such a way that it becomes possible for all the remaining cars to eventually exit the grid.

    What is the minimum value of $k$ that guarantees that Kritesh's job is possible?
\end{problem}

\begin{proof}
    
\end{proof}

\begin{problem}
    Consider an acute triangle $\Delta ABC$. Let $D$ and $E$ be the feet of the altitudes from $A$ to $BC$ and from $B$ to $AC$ respectively.

    Define $D_1$ and $D_2$ as the reflections of $D$ across lines $AB$ and $AC$, respectively. Let $\Gamma$ be the circumcircle of $\Delta AD_1D_2$. 
    Denote by $P$ the second intersection of line $D_1B$ with $\Gamma$, and by $Q$ the intersection of ray $EB$ with $\Gamma$.

    If $O$ is the circumcenter of $\Delta ABC$, prove that $O$, $D$, and $Q$ are collinear if and only if quadrilateral $BCQP$ can be inscribed 
    within a circle.
\end{problem}

\begin{proof}
    
\end{proof}

\end{document}